Blame and Coercion: Together Again for the Second Time

### 2019-10-15 paper.tex
progress

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution represents casts with threesomes, 
a novel cast representation.
They show that their calculus bi-simulates the \lazyUD{} coercion 
calculus in \citet{siek2009exploring} and the Blame Calculus in 
\citet{wadler2009well}. They also prove that threesome is space-efficient as 
well.

@@

	\fbox{$ id( P ) = m $}
	\[
	\begin{array}{rclr}
	\funrule{id(\POOunit)}{\POOunit}{}
	\funrule{id(\POOfun{T_1}{T_2})}{
		\POOfun{id(T_1)}{id(T_2)}
	}{}
	\funrule{id(\POOprod{T_1}{T_2})}{
		\POOprod{id(T_1)}{id(T_2)}
	}{}
	\funrule{id(\POOsum{T_1}{T_2})}{
		\POOsum{id(T_1)}{id(T_2)}
	}{}s
	\end{array}
	\]

@@

>>>>

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution represents casts with threesomes, 
a novel cast representation.
They show that their calculus bisimulates the \lazyUD{} coercion 
calculus in \citet{siek2009exploring} and the Blame Calculus in 
\citet{wadler2009well}. They also prove that threesome is space-efficient as 
well.

@@

	\fbox{$ id( P ) = m $}
	\[
	\begin{array}{rclr}
	\funrule{id(\POOunit)}{\POOunit}{}
	\funrule{id(\POOfun{T_1}{T_2})}{
		\POOfun{id(T_1)}{id(T_2)}
	}{}
	\funrule{id(\POOprod{T_1}{T_2})}{
		\POOprod{id(T_1)}{id(T_2)}
	}{}
	\funrule{id(\POOsum{T_1}{T_2})}{
		\POOsum{id(T_1)}{id(T_2)}
	}{}
	\end{array}
	\]

@@

Figure~\ref{fig:HC-UD}

\begin{figure}
  Composition of hypercoercions \fbox{$ c \fatsemi c = c $}
  \[
  \begin{array}{rclclr}
  c &\fatsemi& \hyperCoercionI{} &=& c\\
  \hyperCoercionI{} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
       \hyperCoercionC{p_2}{m_2}{i_2} \\
  \hyperCoercionC{p_1}{m_1}{\epsilon} &\fatsemi& \hyperCoercionC{\epsilon}{m_2}{i_2} &=&
       \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} \\
  \hyperCoercionC{p_1}{m_1}{!} &\fatsemi& \hyperCoercionC{?^l}{m_2}{i_2} &=&
  \begin{cases}
    \hyperCoercionC{p_1}{m_1 \fatsemi m_2}{i_2} & \text{if } m_1 \smile m_2 \\
    \hyperCoercionC{p_1}{m_1}{\bot^l} & \text{otherwise}
  \end{cases} \\
  \hyperCoercionC{p_1}{m_1}{\bot^l} &\fatsemi& \hyperCoercionC{p_2}{m_2}{i_2} &=&
     \hyperCoercionC{p_1}{m_1}{\bot^l}
  \end{array}
  \]
  Composition of middles \fbox{$m \fatsemi m = m$}
  \[
  \begin{array}{rclclr}  
  \POOunit &\fatsemi& \POOunit &=& \POOunit \\
  c \to d &\fatsemi& c' \to d' &=& (c' \fatsemi c) \to (d \fatsemi d') \\
  c \times d &\fatsemi& c' \times d' &=& (c \fatsemi c') \times (d \fatsemi d') \\
  c + d &\fatsemi& c' + d' &=& (c \fatsemi c') + (d \fatsemi d')
  \end{array}
  \]
  Shallow consistency of middles \fbox{$m \smile m$}
  \[
  \POOunit \smile \POOunit \quad
  (c \to d) \smile (c' \to d') \quad
  (c \times d) \smile (c' \times d') \quad
  (c + d) \smile (c' + d')
  \]

  \fbox{$seq(c,c) = c$}
  \[
  \begin{array}{rclr}
    \funrule{seq(c_1,c_2)}{
      c_1 \fatsemi c_2
    }{}
  \end{array}
  \]

  \fbox{$ id( P ) = m $}
  \[
  \begin{array}{rclr}
    \funrule{id(\POOunit)}{\POOunit}{}
    \funrule{id(\POOfun{T_1}{T_2})}{
		\POOfun{id(T_1)}{id(T_2)}
    }{}
    \funrule{id(\POOprod{T_1}{T_2})}{
		\POOprod{id(T_1)}{id(T_2)}
    }{}
    \funrule{id(\POOsum{T_1}{T_2})}{
		\POOsum{id(T_1)}{id(T_2)}
    }{}
  \end{array}
  \]

  \caption{Lazy UD Hypercoercions}
  \label{fig:HC-UD}
\end{figure}

\begin{figure}
  \fbox{$ \mathit{castToDyn}(P,l) = c$}
  \[
  \begin{array}{rclr}
    \funrule{\mathit{castToDyn}(\star,l,\star)}{ \hyperCoercionI{} }{} 
    \funrule{\mathit{castToDyn}(I,l,\star)}{
      \hyperCoercionC{\epsilon}{\mathit{castToInj}(I,l,I) }{!}
    }{}
    \funrule{\mathit{castToDyn}(P,l,\star)}{
      \hyperCoercionC{\epsilon}{\mathit{castToInj}(P,l,I) }{!}
    }{}
  \end{array}
  \]

  \fbox{$ \mathit{castFromDyn}(P,l) = c$}

  \fbox{$ \mathit{castToInj}(P,l,I) = m$}

  \fbox{$ \mathit{castFromInj}(I,l,P) = m$}

  \fbox{$ cast(T,l,T) = c$}
  \[
  \begin{array}{rclr}
    \funrule{cast(\star,l,T_2)}{ castFromDyn(T_2, l) }{} 
    \funrule{cast(T_1,l,\star)}{ castToDyn(T_2, l) }{} 
    \funrule{cast(\POOunit,l,\POOunit)}{
        \hyperCoercionC{\epsilon}{\POOunit}{\epsilon} }{} 
    cast(T_1 \to T_2,l, T_3 \to T_4) &=&
      \hyperCoercionC{\epsilon}{
         c_1
        \to
         c_2
      }{\epsilon}
      \quad \text{where } c_1 = cast(T_3, l, T_1) \\
      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
    cast(T_1 \times T_2,l, T_3 \times T_4) &=&
      \hyperCoercionC{\epsilon}{
         c_1
        \times
         c_2
      }{\epsilon}
      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)\\
    cast(T_1 + T_2,l, T_3 + T_4) &=&
      \hyperCoercionC{\epsilon}{
         c_1
        +
         c_2
      }{\epsilon}
      \quad \text{where } c_1 = cast(T_1, l, T_3) \\
      &&  \qquad\qquad\qquad \text{and } c_2 = cast(T_2, l, T_4)
  \end{array}
  \]

  \caption{\textit{cast} and auxilliary functions for Lazy UD.}
  \label{fig:HC-UD-cast}
\end{figure}
